---
title: "Stat. 651 Homework 2"
author: "Lydia Gibson"
format: pdf
editor: visual
---

# Chapter 14 Exercises

     
```{r}
library(pacman)

p_load(tidyverse, macleish, lubridate, mdsr, DT, palmerpenguins)
```


## Problem 3: 
The `macleish` package contains weather data collected every 10 minutes in 2015 from two weather stations in Whately, Massachusetts. 

Using the `ggplot2` package, create a data graphic that displays the average temperature over each 10-minute interval (`temperature`) as a function of time (`when`) from the `whately_2015` dataframe. Create annotations to include context about the four seasons: the date of the vernal and autumnal equinoxes, and the summer and winter solstices.


```{r}
#whately_2015 %>% select(when, temperature)

seasons_2015 <- tibble(
    when = (ymd(c("2015 March 20", "2015 June 21", "2015 September 23", "2015 December 21"))),
    season = c("Spring", "Summer", "Fall", "Winter")
)
#seasons_2015

whately_plot <- whately_2015 %>% select(when, temperature) %>% 
  ggplot(aes(y = temperature, x = as.Date(when))) +
  geom_vline(data = seasons_2015, color = "darkgray", aes( xintercept = as.Date(when) ) ) +
  geom_text(data = seasons_2015, aes(y = 33, label = season, hjust = "left")) +
  geom_line(size = 0.3) + 
  geom_smooth() +
  scale_x_date()

whately_plot
```


## Problem 4
Modify the restaurant violations Shiny app so that it displays a table of the number of restaurants within a given type of cuisine along with a count of restaurants (as specified by the dba variable. (Hint: Be sure not to double count. The dataset should include 842 unique pizza restaurants in all boroughs and 281 Caribbean restaurants in Brooklyn.)



```{r echo=FALSE, include=FALSE}
#Violations
#ViolationCodes
#Cuisines

#Join the Cuisines to the Violations dataframe.
mergedViolations <- Violations %>%
  right_join(Cuisines)

#mergedViolations

mergedViolations %>% select(dba, boro, cuisine_description) %>% 
  group_by(cuisine_description) %>% 
  summarize(n = n_distinct(dba)) %>% 
  filter(cuisine_description == "Pizza")

mergedViolations %>% select(dba, boro, cuisine_description) %>% 
  filter(boro == "BROOKLYN") %>% 
  group_by(cuisine_description) %>% 
  summarize(n = n_distinct(dba)) %>% 
  filter(cuisine_description == "Caribbean")
```

[violations_app](https://lgibson7.shinyapps.io/Violations_App/)



## Problem 6
The following code generates a scatterplot with marginal histograms.

```{r}
library(mosaicData)
p <- ggplot(HELPrct, aes(x = age, y = cesd)) +
  geom_point() +
  theme_classic() +
  stat_smooth(method = "loess", formula = y ~ x, size = 2)
ggExtra::ggMarginal(p, type = "histogram", binwidth = 3)

#p
```
Find an example where such a display might be useful. Be sure to interpret your graphical display.

## Problem 7


Using data from the `palmerpenguins` package, create a Shiny app that displays measurements from the `penguins` dataframe. Allow the user to select a species or a gender, and to choose between various attributes on a scatterplot. (Hint: examples of similar apps can be found at the Shiny gallery).


```{r echo=FALSE, include=FALSE}
penguins

names(penguins)

setdiff(names(iris), "Species")

penguins %>% ggplot(aes(x = bill_length_mm, y = bill_depth_mm, color = sex )) +
  geom_point()

penguins %>%  filter(species == "Adelie") %>% 
    ggplot( aes(x = bill_length_mm, y = bill_depth_mm, color = sex)) + geom_point()
```

[Penguin App](https://lgibson7.shinyapps.io/Penguins_App/)


## Problem 8

Create a Shiny app to display an interactive time series plot of the `macleish` weather data. Include a selection box to alternate between data from the `whately_2015` and `orchard_2015` weather stations. Add a selector of dates to include in the display. Do you notice any irregularities?

[macleish App](https://lgibson7.shinyapps.io/Macleish_App/)

