---
title: "Stat. 651 Homework 2"
author: "Lydia Gibson"
date: "2022-10-31"
output: pdf_document
---

# Chapter 14 Exercises

```{r}
install.packages("ggplot2")
library(ggplot2)
```


## Problem 3: 
The `macleish` package contains weather data collected every 10 minutes in 2015 from two weather stations in Whately, Massachusetts. 

Using the `ggplot2` package, create a data graphic that displays the average temperature over each 10-minute interval (`temperature`) as a function of time (`when`) from the `whately_2015` dataframe. Create annotations to include context about the four seasons: the date of the vernal and autumnal equinoxes, and the summer and winter solstices.

## Problem 4
Modify the restaurant violations Shiny app so that it displays a table of the number of restaurants within a given type of cuisine along with a count of restaurants (as specified by the dba variable. (Hint: Be sure not to double count. The dataset should include 842 unique pizza restaurants in all boroughs and 281 Caribbean restaurants in Brooklyn.)





## Problem 6
The following code generates a scatterplot with marginal histograms.

```{r}
p <- ggplot(HELPrct, aes(x = age, y = cesd)) +
  geom_point() +
  theme_classic() +
  stat_smooth(method = "loess", formula = y ~ x, size = 2)
ggExtra::ggMarginal(p, type = "histogram", binwidth = 3)

p
```
Find an example where such a display might be useful. Be sure to interpret your graphical display.

## Problem 7


Using data from the `palmerpenguins` package, create a Shiny app that displays measurements from the `penguins` dataframe. Allow the user to select a species or a gender, and to choose between various attributes on a scatterplot. (Hint: examples of similar apps can be found at the Shiny gallery).



## Problem 8

Create a Shiny app to display an interactive time series plot of the `macleish` weather data. Include a selection box to alternate between data from the `whately_2015` and `orchard_2015` weather stations. Add a selector of dates to include in the display. Do you notice any irregularities?


