---
title: "Stat. 651 Project"
author: "Lydia Gibson"
format: pdf
---

# Project: (due in Canvas Friday December 9, 2022)

Make two statebins using data from FRED US Regioinal Data. Use the socviz Chapter 7 Section 3 as a reference.


```{r message=FALSE}
library(statebins)
library(tidyverse, readr)


```



# 2022 Oct. Unemployment Rate by State (Percent)


```{r warning=FALSE, message=FALSE}
unemployment <- read_csv('/Users/admin/Desktop/Stat651_DataViz/sta651_assignments/completed assignments/stat651_project/Unemployment.csv')


unemployment %>% select("Region Name", "10/1/22") %>%
  mutate(state = `Region Name`,
         unemployed = `10/1/22`
  ) %>% 
  select( unemployed, state) %>% 
  ggplot(aes(state = state, fill = unemployed)) +
geom_statebins() +
  coord_equal() +   
  scale_fill_gradient(name = "Unemployment Rate", 
                      low = munsell::mnsl("5P 7/12"), 
                      high = munsell::mnsl("5P 2/12")) +
  ggtitle("2022 October Unemployment Rate by State (%)")  +
  theme(legend.position = "top")


```



# 2022 October Labor Force Participation Rate by State (Percent)

A state's labor-force participation rate is the number of all employed and unemployed workers divided against the state's civilian population. Differences between monthly seasonally-adjusted and not-seasonally-adjusted labor force participation rates are determined by the seasonal components of the LAUS labor force levels.


```{r warning=FALSE, message=FALSE}

labor_force <- read_csv('/Users/admin/Desktop/Stat651_DataViz/sta651_assignments/completed assignments/stat651_project/Labor_Force.csv')


labor_force %>% select("Region Name", "10/1/22") %>%
  mutate(state = `Region Name`,
         lab_force = `10/1/22`
  ) %>% 
  select( lab_force, state) %>% 
  ggplot(aes(state = state, fill = lab_force)) +
  geom_statebins() +
    coord_equal() +
    scale_fill_gradient(name = "Labor Force Participation", 
                     low = munsell::mnsl("5P 7/12"), 
                    high = munsell::mnsl("5P 2/12")) +
    ggtitle("2022 Oct. Labor Force Participation Rate by State (%)") +
    theme(legend.position = "top")

  


```

